DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-12-14 manuscript/manuscript.Rmd
addressing comments about suppl data

We illustrate the DateLife workflow using a family within the Passeriform birds encompassing the true finches, Fringillidae, as case study. The first example analyses 6 bird species and shows all steps of the workflow The second example is an analysis of 289 species in the family Fringillidae that are included in the NCBI taxonomy.
<!--We used `r cite_r("r-references.bib")` for all our analyses.-->

@@

Code used to generate all versions of this manuscript, the biological examples, as well as the benchmark of functionalities are available at [datelifeMS1](https://github.com/LunaSare/datelifeMS1), [datelife_examples](https://github.com/LunaSare/datelife_examples), and [datelife_benchmark](https://github.com/LunaSare/datelife_benchmark) repositories in LLSR's GitHub account.

>>>>

We illustrate the DateLife workflow using a family within the Passeriform birds encompassing the true finches, Fringillidae, as case study. On a small example, we analysed 6 bird species, and results from each step of the workflow are shown in Fig. \ref{fig:figure2}. As a second example, we analysed 289 bird species in the family Fringillidae that are included in the NCBI taxonomy. The resulting summary chronogram is shown in Fig. \ref{fig:fringillidages}, and results from previous steps of the workflow are available as Supplementary Figures.
<!--We used `r cite_r("r-references.bib")` for all our analyses.-->

@@

Supplementary material, including code, biological examples and benchmark results data files and online-only appendices, can be found in the Dryad data repository (<https://doi.org/10.5061/dryad.cnp5hqc6w>), as well as in the GitHub repositories used to develop the reproducible manuscript (<https://doi.org/10.5281/zenodo.7435094>), the biological examples (<https://doi.org/10.5281/zenodo.7435101>), and the software benchmark (<https://doi.org/10.5281/zenodo.7435106>).
